### 2015-10-01 manuscript.Rnw
various edits

<<get_taxa, cache=TRUE>>=
taxa <- tnrs_match_names(names = c("Escherichia coli",
                                   "Chlamydomonas reinhardtii",
                                   "Drosophila melanogaster",
                                   "Arabidopsis thaliana",
                                   "Rattus norvegicus",
                                   "Mus musculus",
                                   "Cavia porcellus",
                                   "Xenopus laevis",
                                   "Saccharomyces cervisae",
                                   "Danio rerio"))
@

The function \texttt{tnrs\_match\_names} returns a data frame that lists the Open
Tree identifiers as well as other information to help users to ensure that the
taxa matched are the correct ones. Here, there is no ambiguity in the taxa
matched, however, as the Open Tree Taxonomy includes taxa from bacteria, plants,
and animals that are regulated by different nomenclatural codes (ICNP, ICN and
ICZN respectively), OTL and \texttt{rotl} provide tools to deal with potential
hemihomonyms. For instance, the argument \texttt{context\_name} can be used to
limit potential matches to a taxonomic group. The function
\texttt{tnrs\_contexts} provides a list of possible taxonomic contexts. When this
strategy cannot be used in case the tree encompasses multiple domains, the
functions \texttt{inspect} and \texttt{update} list alternative matches for a
taxon name, and replace it in the results, respectively. An example of this
approach is provided in the vignette ``How to use rotl?'' that accompanies the
package.
By default, approximate matching is enabled when attempting to match taxonomic
names to their Open Tree Taxonomy identifiers. Additionally, taxonomic synonyms
are included in the Open Tree Taxonomy allowing researchers to match correct
identifiers for taxon names that might include misspellings or synonyms. These
features will facilitate the tedious data cleaning process often needed when
matching taxon names. In the example provided, both \textit{Escherichia coli}
and \textit{Saccharomyces cerevisiae} are misspelled but OTL's TNRS finds the
correct match for these taxa.

@@

Currently only one study focused on this family is available from OTL, and a
single tree is associated with it. We can then retrieve the identifiers and pass
them to the function \texttt{get\_study\_tree} to have the tree in memory:

@@

When more than one tree is available for a given study, the function
\texttt{list\_trees} returns a list to retrieve the tree identifiers for each
study easily. Alternatively, the function \texttt{get\_study} returns all the
trees associated with a particular study. Additional details about the study can
be obtained using the function \texttt{get\_study\_meta}.

>>>>

<<get_taxa, cache=TRUE>>=
taxa <- tnrs_match_names(names = c("Escherichia colli",
                                   "Chlamydomonas reinhardtii",
                                   "Drosophila melanogaster",
                                   "Arabidopsis thaliana",
                                   "Rattus norvegicus",
                                   "Mus musculus",
                                   "Cavia porcellus",
                                   "Xenopus laevis",
                                   "Saccharomyces cervisae",
                                   "Danio rerio"))
@

The function \texttt{tnrs\_match\_names} returns a data frame that lists the
Open Tree identifiers as well as other information to help users to ensure that
the taxa matched are the correct ones. Here, there is no ambiguity in the taxa
matched, however, as the Open Tree Taxonomy includes taxa from bacteria, plants,
and animals that are regulated by different nomenclatural codes (ICNP, ICN and
ICZN respectively), OTL and \texttt{rotl} provide tools to deal with potential
hemihomonyms. The argument \texttt{context\_name} can be used to limit potential
matches to a taxonomic group (see the function \texttt{tnrs_contexts} for a list
of possible options).  When this strategy cannot be used in case the tree
encompasses multiple domains (as in the present example), the function
\texttt{inspect} lists alternative matches for a taxon name, and \texttt{update}
replaces it in the results. An example of this approach is provided in the
vignette ``How to use rotl?'' that accompanies the package.

By default, approximate matching is enabled when attempting to match taxonomic
names to their Open Tree Taxonomy identifiers. Additionally, taxonomic synonyms
are included in the Open Tree Taxonomy allowing researchers to match correct
identifiers for taxon names that might include misspellings or synonyms. These
features will facilitate the tedious data cleaning process often needed when
matching taxon names. In the example provided, both \textit{Escherichia coli}
and \textit{Saccharomyces cerevisiae} are misspelled but OTL's TNRS finds the
correct match for these taxa.

@@

Currently only one study focused on this family is available from OTL, and a
single tree is associated with it. We can then retrieve the study and tree
identifiers, and pass them to the function \texttt{get\_study\_tree} to have the
tree in memory:

@@

When more than one tree is available for a given study, the function
\texttt{list\_trees} returns a list containing the tree identifiers for each
study easily. Alternatively, the function \texttt{get\_study} returns all the
trees (by default as \texttt{ape::phylo} objects) associated with a particular
study. Additional details about the study (i.e., its metadata) can be obtained
using the function \texttt{get\_study\_meta}.
